---
title: "Assignment 2"
author: "Penny Jiang"
date: "02/17/2023"
output: html_document
---

# Import a stata file into R

```{r}
library("haven")
# clear your memory 
rm(list=ls()) 
TEDS_2016 <- read_dta ("https://github.com/datageneration/home/blob/master/DataProgramming/data/TEDS_2016.dta?raw=true")
```

#Assgn label to the values

```{r}
TEDS_2016$Tondu<-as.numeric(TEDS_2016$Tondu,labels=c("Unification now","Status quo,unif.infuture","Statusquo,decidelater","Statusquoforever","Statusquo,indep.infuture","Independencenow","No response"))
```

#Check the variable

```{r}
attach(TEDS_2016) 
head(Tondu) 
tail(Tondu)
```

#Run a frequency table of the Party ID variable using the descr package #install.packages("descr")

```{r}
library(descr) 
freq(TEDS_2016$Tondu)
```

# Plot the Tondu variable

```{r}
library(ggplot2) 
ggplot(TEDS_2016, aes(Tondu)) + 
  geom_bar()
```

# Plot the Tondu variable

```{r}
ggplot(TEDS_2016, aes(Tondu)) + geom_bar(aes(y = (..count..)/sum(..count..),fill=Tondu)) + scale_y_continuous(labels=scales::percent) + ylab("Party Support (%)") + xlab("Tondu Status") + theme_bw()
```

\# From the chart, there is no values for the category of 7.5 for Tondu.

#It is obvious that there are missing data in the dataset. We can try to impute them (e.g. average imputation or common point imputation). There are several dummy variables in the dataset, "notetsai" is one of the dummy variables.

#For numerical variables such as gender, age, income and education etc., we can use liner regression model to find the correlate between them with Tondu or use scatterplots or bar plot as a method of visualization to find the relationship between those independent variables and dependent variable
