---
title: "Logistic regression with TEDS_2016"
author: "Penny Jiang"
date: "4/1/2023"
output: html_document
---
---
  
#### Use the TEDS2016 dataset to run a logit (logistic regression) model using female as sole predictor. 
#### The dependent variable is the vote (1-0) for Tsai Ing-wen, the female candidate for the then opposition party Democratic Progressive Party (DPP). 
#### Access the data set using the following codes:
```{r}
library(haven)
TEDS_2016<-read_stata("https://github.com/datageneration/home/blob/master/DataProgramming/data/TEDS_2016.dta?raw=true")
```

#### Check the dataset
```{r}
names(TEDS_2016)
```

#### Logistic regression
```{r}
teds.fit=glm(votetsai~female, data=TEDS_2016,family=binomial)
summary(teds.fit)
```
#### Female voters are not likely to vote for President Tsai becasue the coefficient for "female" (-0.06)is not statistically significant.

#### Add in party ID variables (KMT, DPP) and other demographic variables (age, edu, income) to test the model
```{r}
teds.fit2=glm(votetsai~female+KMT+DPP+Age+edu+income,
              data=TEDS_2016,family=binomial)
summary(teds.fit2)
```

#### "Female" is still not statistically significant; while "KMT", "DPP", "Age" and "edu" are all statistically significant. The results indicate that KMT party followers are less likely to vote for Tsai Ing-wen, whereas DPP party members are more likely to do so. Age and education are negatively related to the DV, implying that those that are younger and less educated are more likely to vote for Tsai Ing-wen.


#### Add more variables to further test the model
```{r}
teds.fit3=glm(votetsai~female+KMT+DPP+Age+edu+income+Independence+Econ_worse+Govt_dont_care+Minnan_father+Mainland_father+Taiwanese,
              data=TEDS_2016,family=binomial)
summary(teds.fit3)
```
#### After adding in new variables, age and education become statistically insignificant. The other two variables (KMT and DPP) are still significance. "Independence," "Mainland_father" and "Econ_worse" also show statistically significance in the model.

